Safe Transferable Regions

### 2016-07-03 paper/implementation.tex
Comments on un-safety detection.

Our experience with Naiad benchmarks suggests that, although our
approach cannot statically enforce memory safety, it is nonetheless
useful, particularly because the static verification comes at no
additional cost to the developer. If the developer is satisfied with
the confidence gained by static verification, she may even choose to
turn the runtime safety checks off. Since we did not implement code
generation in \namec, we could not measure the runtime overhead of
checks needed to enforce safety. However, the number of LOC peforming
operations on \C{Region} objects relative to the total LOC never
exceeds 8\% in Naiad benchmarks. 
% \C{SelectVertex}, for example, contains one each of
% \C{open} and \C{transfer} operations on one region in its 45LOC,
% whereas, \C{JoinVertex} contains 5 \C{open}s, 2 \C{transfer}s, and 1
% \C{free} operation.

>>>>

\dv{Hmmmm what is \C{inMsg.payload[i]} in this case? Is it an object? The example
  demonstrates that we should really have passed in a region that stored other
  transferrable regions inside, i.e. we should proably make the \C{inMsg.payload[i]} a
  region itself. This way we don't have to pay the cost of clone. I think that might be
  an interesting additional discussion in this paragraph. Otherwise I am left as a reader
  with this bittersweat feeling that ``ok you fixed it but you introduced a copy''. But if
  the payload was also on it own transferrable region we would be fine right? We probably
  need a \C{GiveUp} primitive of a region too as we will transfer only the root transferrable
  region (\C{inMsg}) but we want to declare that we've given up ownership on all the nested
  ones too.}

Our experience with Naiad benchmarks suggests that, although our
approach cannot statically enforce memory safety, \dv{Valid point,
  also worth re-visiting in the light of the above?}
it is nonetheless useful, particularly because the static verification comes at no
additional cost to the developer. If the developer is satisfied with
the confidence gained by static verification, she may even choose to
turn the runtime safety checks off. Since we did not implement code
generation in \namec, we could not measure the runtime overhead of
checks needed to enforce safety. However, the number of LOC peforming
operations on \C{Region} objects relative to the total LOC never
exceeds 8\% in Naiad benchmarks. 
% \C{SelectVertex}, for example, contains one each of
% \C{open} and \C{transfer} operations on one region in its 45LOC,
% whereas, \C{JoinVertex} contains 5 \C{open}s, 2 \C{transfer}s, and 1
% \C{free} operation.
